%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
\input{constants/configurations.tex}
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
\definecolor{awesome}{HTML}{\COLOR}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{\HIGHLIGHT_TITLES}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
\input{constants/personal-information.tex}
% Available options: circle|rectangle,edge/noedge,left/right

%\photo[right,rectangle,noedge]{./photo/photo.jpg}
\name{\FIRST_NAME}{\LAST_NAME}
\position{\POSITION}
%\address{\ADRESS}
\mobile{\MOBILE}
\email{\EMAIL}
\github{\GITHUB}
\linkedin{\LINKEDIN}
\homepage{\HOMEPAGE}
% \gitlab{\GITLAB}
% \stackoverflow{\SO_ID}{\SO_NAME}
% \twitter{\TWITTER}
% \skype{\SKYPE}
% \reddit{\REDDIT_ID}
% \medium{\MEDIUM_ID}
% \googlescholar{\GOOGLE_SCHOLAR_ID}{\GOOGLE_SCHOLAR_NAME}
% \extrainfo{\EXTRA_INFO}

\quote{\QUOTE}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer}
% How the letter is opened
\letteropening{Dear Mr./Ms./Dr. LastName,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {\FIRST_NAME \LAST_NAME~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
Passionate software engineer eager to embrace new technologies and contribute to the ever-evolving IT landscape. Throughout my career, I have had the privilege to work in diverse industries, gaining invaluable insights and experiences that have enriched my problem-solving abilities and broadened my horizons.
With a degree in electrical engineering, I have acquired a deep understanding of the underlying principles that power modern technology. Beyond technical skills, my background has ingrained in me a strong foundation in problem analysis and a detail-oriented approach to projects. This, coupled with my passion for software engineering, allows me to deliver high-quality, scalable, and reliable solutions that meet and exceed expectations.


\lettersection{Why Google?}
Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. Aliquam adipiscing nibh ut odio sodales et pulvinar tortor laoreet. Mauris a accumsan ligula. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Suspendisse vulputate sem vehicula ipsum varius nec tempus dui dapibus. Phasellus et est urna, ut auctor erat. Sed tincidunt odio id odio aliquam mattis. Donec sapien nulla, feugiat eget adipiscing sit amet, lacinia ut dolor. Phasellus tincidunt, leo a fringilla consectetur, felis diam aliquam urna, vitae aliquet lectus orci nec velit. Vivamus dapibus varius blandit.

\lettersection{Why Me?}
Why Me? Allow me to confess - this cover letter was crafted with the help of ChatGPT, showcasing my resourcefulness in leveraging cutting-edge technologies. As a software engineer, I believe in embracing innovation, and with me on your team, you gain a valuable asset—a fusion of human expertise and AI-powered humor. 
I am committed to delivering high-quality results and fostering a collaborative and productive work atmosphere. My effective communication skills facilitate seamless interaction with cross-functional teams, enabling us to achieve shared goals.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
